---
title: "Oracle"
author: "Aadish Chopra"
date: "10/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE)
```


Assume, Average Rating to be the selection criterion (higher is better).

 

Find  Top 3 movies

by Occupation

by Genre

by Occupation, Genre

by Age group  [ <=6, <=12 <=18, <=30, <=50, 50+]

Find Top 3 genres released  (release date )in Summer [May – July]

For each genre, find co-occurring (top 2 )genres

 

Extra Credit:  For each user, find another one with similar preference [same movies, similar ratings]


# Extracting the Data

1. We will use the links present to extract the data 
2. Column Names from the readme file

```{r}

U.Data<-read.csv("http://files.grouplens.org/datasets/movielens/ml-100k/u.data",header = FALSE,sep = "\t",col.names = c("User_ID","Item_ID","Rating","TimeStamp"))

U.Item<-read.csv("http://files.grouplens.org/datasets/movielens/ml-100k/u.item",header=FALSE,sep="|",col.names = c("movie_id","movie_title","release_date","video_release_date","IMDb URL", "unknown","Action","Adventure","Animation","Children's","Comedy","Crime",    "Documentary","Drama","Fantasy","Film-Noir","Horror","Musical","Mystery","Romance"     ,"Sci-Fi","Thriller","War","Western"))

U.Item<-U.Item[,-4]

U.User<-read.csv("http://files.grouplens.org/datasets/movielens/ml-100k/u.user",header=FALSE,sep="|",col.names = c("User_ID","age","gender","occupation","zip code"))


U.Genres<-read.csv("http://files.grouplens.org/datasets/movielens/ml-100k/u.genre",header=FALSE,sep="|",col.names = c("genre","Number"))



```

1. U.Item had no data for video release date which had to be removed


# Programming Assignments

Note: Assume, Average Rating to be the selection criterion (higher is better).

####  Find  Top 3 movies by Occupation


```{r}
#merge the dataset

UData_User<-merge(U.Data,y = U.User,by = "User_ID")

# group by occupation,item_id 
groupby<-by(UData_User,list(UData_User$occupation,UData_User$Item_ID),FUN = function(x) 
  {
  data.frame(occupation=unique(x$occupation),
  Item_ID=unique(x$Item_ID),
  mean_rating=mean(x$Rating),
  Count_Item_ID=nrow(x)
  )
  })

Top3Occupation<-do.call(rbind,groupby)
Top3Occupation<-Top3Occupation[with(Top3Occupation,order(occupation,-mean_rating,-Count_Item_ID)),]


# pick top 3 

Top3Occupation<-by(Top3Occupation,list(Top3Occupation$occupation),head,n=3) 
Top3Occupation<-do.call(rbind.data.frame,Top3Occupation)



```

Assumptions:

1. Ties are broken by counts. 
2. Secondary level ties are ignored and the item which comes first is selected

####  Find  Top 3 movies by Genre

```{r}



```



