---
title: "Oracle"
author: "Aadish Chopra"
date: "10/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE)
```


Assume, Average Rating to be the selection criterion (higher is better).

 

Find  Top 3 movies

by Occupation

by Genre

by Occupation, Genre

by Age group  [ <=6, <=12 <=18, <=30, <=50, 50+]

Find Top 3 genres released  (release date )in Summer [May – July]

For each genre, find co-occurring (top 2 )genres

 

Extra Credit:  For each user, find another one with similar preference [same movies, similar ratings]


# Extracting the Data

1. We will use the links present to extract the data 
2. Column Names from the readme file

```{r}

U.Data<-read.csv("http://files.grouplens.org/datasets/movielens/ml-100k/u.data",header = FALSE,sep = "|",col.names = c("User_ID","Item_ID","Rating","TimeStamp"))

U.Item<-read.csv("http://files.grouplens.org/datasets/movielens/ml-100k/u.item",header=FALSE,sep="|",col.names = c("movie_id","movie_title","release_date","video_release_date","IMDb URL", "unknown","Action","Adventure","Animation","Children's","Comedy","Crime",    "Documentary","Drama","Fantasy","Film-Noir","Horror","Musical","Mystery","Romance"     ,"Sci-Fi","Thriller","War","Western"))

U.Item<-U.Item[,-4]

U.User<-read.csv("http://files.grouplens.org/datasets/movielens/ml-100k/u.user",header=FALSE,sep="|",col.names = c("User_ID","age","gende","occupation","zip code"))


U.Genres<-read.csv("http://files.grouplens.org/datasets/movielens/ml-100k/u.genre",header=FALSE,sep="|",col.names = c("genre","Number"))



```

1. U.Item had no data for video release date which had to be removed